  First and foremost, I would like to thank my advisor Rayan Saab for all of his involvement in my academic career.  In my first year of graduate school, it was his class on compressed sensing that convinced me to switch into the computational math track, which in turn is where I found the material and the problems that motivated me to continue in academic research.  Since then, his support -- in our many hours of teamwork at the whiteboard; his connections to problems, authors, conferences, and collaborators; and the simple things such as critiques of my writing and talks -- was uniquely indispensable in shaping the environment in which I found my place as a researcher.  I am immensely thankful for the inspiration of his talent and energetic leadership.

  I would also like to thank Mark Iwen and Aditya Viswanathan, our two co-authors and collaborators on the subjects covered in this thesis.  The ground that they broke on this new strain of phase retrieval proved to be incredibly fruitful, and I am thankful for being welcomed as a contributor to their ongoing research efforts.  This partnership was foundational to my beginnings in research and much of my subsequent progress, and I am deeply indebted to their generous spirit of academic camaraderie.  Chapter \ref{ch:our_model}, \crefrange{sec:intro}{sec:AltPerturbBounds}, in full, is a reprint of material published with Iwen and Viswanathan as published in Applied and Computational Harmonic Analysis 2018.  Chapter \ref{ch:base_model} section \ref{sec:spie_2d}, in part, is a reprint of material published with these authors in the Proceedings of SPIE vol.~10394, 2017.

  
